SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-06 scipy-1.0/covlett.tex
MAINT: cover letter spacing improvements
* reduce wasted vertical space in the letter
so that we do not overflow to a second page;
also, include link to insructions for adjusting
this spacing
MAINT: apply Stefan's revision to cover letter

\documentclass[10pt,stdletter,dateno]{newlfm}
\usepackage{kpfonts}
\usepackage{url}

@@

\newlfmP{headermarginskip=10pt}
\newlfmP{sigsize=50pt}
\newlfmP{dateskipafter=20pt}
%\newlfmP{addrfromphone}
%\newlfmP{addrfromemail}
%\PhrPhone{Phone}
%\PhrEmail{Email}

@@

We have specifically chosen \emph{Scientific Reports} because
the breadth of acceptable topics matches the variety of algorithms
our library provides. High-profile manuscripts citing SciPy range
from the biosciences to recent reports on gravitational waves and
black holes. These citations target a website, and we now think
it is well past time that our mature library has a peer-reviewed
journal article describing it.

>>>>

\documentclass[10pt,stdletter,dateno]{newlfm}

% to adjust vertical spacing properties of
% newlfm class see: https://tex.stackexchange.com/a/65533/43006
\topmarginsize{2mm}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}

\usepackage{kpfonts}
\usepackage{url}

@@

\newlfmP{headermarginskip=10pt}
\newlfmP{sigsize=30pt}
\newlfmP{dateskipafter=20pt}
%\newlfmP{addrfromphone}
%\newlfmP{addrfromemail}
%\PhrPhone{Phone}
%\PhrEmail{Email}

@@

We have specifically chosen \emph{Scientific Reports} because
the breadth of acceptable topics matches the variety of algorithms
our library provides. High-profile manuscripts citing SciPy range
from the biosciences to recent reports on gravitational waves and
black holes. Lacking a better alternative, these citations all point
to the SciPy website; instead, we think the package now merits a
formal publication in a highly visible journal.
